---
output: html_document
editor_options: 
  chunk_output_type: console
---
# All analyses

## Things we can do without access to IPD

### Adjusting p-value for decision at hand

```{r}

glms <- cache_rds({lst(
  cld = glm(cld ~ trt, family = binomial, data = dat),
  mort = glm(mort ~ trt, family = binomial, data = dat)
)}, dir = cache, file = "marginal_glms") 

map(glms, summary)
```


```{r}
conf_vector <- seq(from = 0.95, to = 0.7, length.out = 10)

power <- FALSE
i <- 1
while(power == FALSE){

  pwr <- epiR::epi.sscc(OR = 0.7, # Coincides to risk difference of 8% based on 36% baseline risk
               p0 = 0.36,
               n = 1350,
               conf.level = conf_vector[[i]],
               power = NA)
  
  power = pwr$power >= 0.9
  i = i + 1
}

new_alpha <- 1 - conf_vector[[i]]

```


Before we get into more direct decision theory approaches, one simple way we can
make decisions a little more local is just by re-evaluating our values of alpha
and beta. Let's use CLD as a rough proxy for risk of disability and say that
maybe locally we are willing to risk more false positives in order to decrease
our possibility of missing a true effect. Instead of the default assumption that
a false positive is four times worse than a false negative let's say in this
case we decide that the potential harm from this intervention is such that we're
willing to risk a two to one trade off. If we fix the sample size and assume we
woudn't want to miss a risk difference of 8% (OR of 0.7) then this would equate
to a p-value of `r round(new_alpha, 2)`.

This equates to a decision rule that "If I can be confident in the direction of
the effect" using alpha/beta to weigh risks of false negative/positive then you
act "as if" there is/is not a difference.

### MCDA from marginals

In the first step we will need marginal probabilities with uncertainty from each
outcome we'd like to include in the mcda. An easy way to do this is just to run
a glm and then sample predicted probabilities from the variance covariance matrix.

```{r}
outs <- purrr::set_names(c("mort", "sev_ivh", "sepsis", "cld", "nec"))

mcda_marg_dat <- mcda_prep(outs, data = pres_dat)


mcda_marg <- cache_rds({
  
  lst(dat = mcda_marg_dat,
      mcda =  do_mcda(5, mcda_marg_dat))
  
 },
                       dir = cache, file = "marg_mcda")
```


## Approaches that we need IPD for

### Ordinal model

An alternative approach might be to arrange outcomes from best to worse and then
use an ordinal model to run the analysis interpreting the treatment effect as
a kind of improvement in quasi utility. 

```{r}
ord <- c("sepsis", "nec", "cld", "sev_ivh", "mort")



dat_ord_orig <- make_ord(data = pres_dat, name = "ord1", order = ord)

dat_ord_synth <- make_ord(data = pres_dat_syn, name = "ord1", order = ord)


ord_models <- cache_rds({
  lst(
  orig = rms::orm(ord1 ~ trt, data = dat_ord_orig),
  synth = rms::orm(ord1 ~ trt, data = dat_ord_synth)
)
}, dir = cache, file = "ord_models") 


ord_models


```


### MCDA with conditional

A drawback of the ordinal model is that it doesn't let us specify how much worse
one outcome is than another. We can extend the marginal MCDA to account for 
combinations of outcomes being worse by leveraging our synthetic dataset. This 
could be extended further by having non-linear partial utilities or other
considerations.

```{r}
outs_prep <- c("mort", "sepsis", "nec", "cld_ivh")

mcda_comb_list <- cache_rds({

  set.seed(124)
  mcda_comb_orig_dat <- mcda_prep(outs_prep, data = pres_dat)
  
  mcda_comb_orig <- do_mcda(4, mcda_comb_orig_dat)
  
  set.seed(124)
  
  mcda_comb_syn_dat <- mcda_prep(outs_prep, data = pres_dat_syn)
  mcda_comb_syn <- do_mcda(4, mcda_comb_syn_dat)

  lst(orig_dat =  mcda_comb_orig_dat,
      orig_mcda =  mcda_comb_orig,
      comb_dat = mcda_comb_syn_dat,
      comb_mcda = mcda_comb_syn)
}, dir = cache, file = "comb_mcdas")


```

